ms_results

### 2023-02-08 ms_figures.Rmd
updating with foreign export stats

library(tidyverse)
library(countrycode)
library(circlize)
library(here)
library(ggpubr)
library(kableExtra)
library(DBI)
library(janitor)
library(viridis)
library(broom)
library(exploreARTIS)
library(vegan)
library(tidytext)
library(cowplot)
library(scales)
```

@@

```{r fig4_old, fig.height = 7, fig.width = 7}
fig4 <- ggarrange(fig4a,
                  fig4b,
          ggarrange(fig4d,
                    fig4e,
                    nrow = 1,
                    common.legend = TRUE, 
                    legend = "bottom",
                    labels = c("c", "d")),
          nrow = 3,
          labels = c("a", "b", "")
          )

@@

```{r regional_sankey, fig.height = 2, fig.width = 2}
# regional_artis <- read.csv(file.path(datadir, "regional_artis_by_source.csv"))
# plot_regional_sankey_method_habitat(regional_artis, 2019, 2019)

@@

marine_cap_p <- marine_cap_regions %>%
  ggplot(aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               value = value,
               label = node)) +
    geom_sankey(flow.alpha = 0.6) +
    scale_fill_manual(values = region6_palette) +
    geom_sankey_label(size = 3, color = "white", fill = "gray40") +
    theme_sankey(base_size = 18) +
  labs(x = NULL) +
    #labs(title = "Marine", x = NULL, y = "CAPTURE") +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(c(0,0,0,0), unit = "mm")
    )

@@

marine_aqua_p <- marine_aqua_regions %>%
  ggplot(aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               value = value,
               label = node)) +
    geom_sankey(flow.alpha = 0.6) +
    scale_fill_manual(values = region6_palette) +
    geom_sankey_label(size = 3, color = "white", fill = "gray40") +
    theme_sankey(base_size = 18) +
  labs(x = NULL) +
    #labs(title = "Marine", x = NULL, y = "CAPTURE") +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(c(0,0,0,0), unit = "mm")
    )

@@

inland_cap_p <- inland_cap_regions %>%
  ggplot(aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               value = value,
               label = node)) +
    geom_sankey(flow.alpha = 0.6) +
    scale_fill_manual(values = region6_palette) +
    geom_sankey_label(size = 3, color = "white", fill = "gray40") +
    theme_sankey(base_size = 18) +
  labs(x = NULL) +
    #labs(title = "Marine", x = NULL, y = "CAPTURE") +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(c(0,0,0,0), unit = "mm")
    )

@@

inland_aqua_p <- inland_aqua_regions %>%
  ggplot(aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               value = value,
               label = node)) +
    geom_sankey(flow.alpha = 0.6) +
    scale_fill_manual(values = region6_palette) +
    geom_sankey_label(size = 3, color = "white", fill = "gray40") +
    theme_sankey(base_size = 18) +
  labs(x = NULL) +
    #labs(title = "Marine", x = NULL, y = "CAPTURE") +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(c(0,0,0,0), unit = "mm")
    )

@@

>>>>

library(tidyverse)
library(countrycode)
library(circlize)
library(here)
library(ggpubr)
library(kableExtra)
library(DBI)
library(janitor)
library(viridis)
library(broom)
library(exploreARTIS)
library(vegan)
library(tidytext)
library(cowplot)
library(scales)
library(ggsankey)
library(ggpubr)
```

@@

```{r fig4_old, fig.height = 7, fig.width = 7, eval = FALSE}
fig4 <- ggarrange(fig4a,
                  fig4b,
          ggarrange(fig4d,
                    fig4e,
                    nrow = 1,
                    common.legend = TRUE, 
                    legend = "bottom",
                    labels = c("c", "d")),
          nrow = 3,
          labels = c("a", "b", "")
          )

@@

```{r regional_sankey, fig.height = 2, fig.width = 2}
regional_artis <- read.csv(file.path(datadir, "regional_artis_by_source.csv"))
# plot_regional_sankey_method_habitat(regional_artis, 2019, 2019)

@@

marine_cap_p <- marine_cap_regions %>%
  ggplot(aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               value = value,
               label = node)) +
    geom_sankey(flow.alpha = 0.6) +
    scale_fill_manual(values = region_colors) +
    geom_sankey_label(size = 3, color = "white", fill = "gray40") +
    theme_sankey(base_size = 18) +
  labs(x = NULL) +
    #labs(title = "Marine", x = NULL, y = "CAPTURE") +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(c(0,0,0,0), unit = "mm")
    )

@@

marine_aqua_p <- marine_aqua_regions %>%
  ggplot(aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               value = value,
               label = node)) +
    geom_sankey(flow.alpha = 0.6) +
    scale_fill_manual(values = region_colors) +
    geom_sankey_label(size = 3, color = "white", fill = "gray40") +
    theme_sankey(base_size = 18) +
  labs(x = NULL) +
    #labs(title = "Marine", x = NULL, y = "CAPTURE") +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(c(0,0,0,0), unit = "mm")
    )

@@

inland_cap_p <- inland_cap_regions %>%
  ggplot(aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               value = value,
               label = node)) +
    geom_sankey(flow.alpha = 0.6) +
    scale_fill_manual(values = region_colors) +
    geom_sankey_label(size = 3, color = "white", fill = "gray40") +
    theme_sankey(base_size = 18) +
  labs(x = NULL) +
    #labs(title = "Marine", x = NULL, y = "CAPTURE") +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(c(0,0,0,0), unit = "mm")
    )

@@

inland_aqua_p <- inland_aqua_regions %>%
  ggplot(aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               value = value,
               label = node)) +
    geom_sankey(flow.alpha = 0.6) +
    scale_fill_manual(values = region_colors) +
    geom_sankey_label(size = 3, color = "white", fill = "gray40") +
    theme_sankey(base_size = 18) +
  labs(x = NULL) +
    #labs(title = "Marine", x = NULL, y = "CAPTURE") +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(c(0,0,0,0), unit = "mm")
    )

@@

```{r dom_source_ts, fig.height = 4, fig.width = 6}
dom_source_ts <- read.csv(file.path(datadir, "dom_source_ts.csv"))

dom_source_ts_p <- dom_source_ts %>%
  filter(dom_source != "error export") %>%
  ggplot(aes(x = year, y = live_weight_t / 1000000, color = dom_source)) +
  geom_line() +
  scale_color_manual(values = c("#D38F35", "#114F59")) +
  theme_bw() +
  labs(x = "", y = "Live weight\nmillion tonnes", color = "Source") +
  theme(
    legend.position = "bottom",
    legend.box.margin=margin(t = -25)
  )

dom_source_ts_p
```

```{r dom_source_by_habitat_ts, fig.height = 4, fig.width = 7}
dom_source_by_habitat_method <- read.csv(file.path(datadir, "dom_source_by_habitat_method.csv"))

dom_source_by_habitat_method_p <- dom_source_by_habitat_method %>%
  # Set factor levels
  mutate(habitat_method = factor(habitat_method, levels = c("marine capture", "inland capture",
                                                            "marine aquaculture", "inland aquaculture",
                                                            "unknown" ))) %>%
  ggplot(aes(x = year, y = live_weight_t / 1000000, fill = habitat_method)) +
  geom_area() +
  scale_fill_manual(values = habitat_source_colors) +
  theme_bw() +
  labs(x = "", y = "Live weight\nmillion tonnes", fill = "Source") +
  facet_wrap(~dom_source) +
  theme(
    legend.position = "bottom",
    panel.spacing = unit(5, "mm"),
    legend.box.margin=margin(t = -15)
  )

dom_source_by_habitat_method_p
```

```{r dom_source_overview, fig.height = 5, fig.width = 7}
ggarrange(
  dom_source_ts_p,
  dom_source_by_habitat_method_p,
  nrow = 2,
  labels = c("a", "b")
)

ggsave("dom_source_2019_overview.png")
```

```{r top_processing_countries_by_source, fig.height = 4, fig.width = 6}

top_processing_by_source <- read.csv(file.path(datadir, "top_processing_by_source.csv"))

top_processing_by_source %>%
  filter(year == 2019) %>%
  # Set factor levels
  mutate(habitat_method = factor(habitat_method, levels = c("marine capture", "inland capture",
                                                            "marine aquaculture", "inland aquaculture",
                                                            "unknown" ))) %>%
  ggplot(aes(x = live_weight_t / 1000000, y = reorder(exporter_iso3c, ranking), fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  theme_bw() +
  labs(x = "Live weight million tonnes", y = "", fill = "Source") +
  facet_wrap(~habitat_method, scales = "free_y") +
  theme(legend.position = "none")

ggsave("foreign_exports_2019_by_source.png")
```

### 2023-02-08 ms_results.Rmd
updating with foreign export stats

@@

>>>>

```{r dom_source_stats}
dom_source_ts <- read.csv(file.path(datadir, "dom_source_ts.csv"))
foreign_exports_1996 <- dom_source_ts %>%
  filter(dom_source == "foreign export") %>%
  filter(year == 1996) %>%
  pull(live_weight_t)

foreign_exports_2019 <- dom_source_ts %>%
  filter(dom_source == "foreign export") %>%
  filter(year == 2019) %>%
  pull(live_weight_t)

foreign_exports_percent_change <- 100 * (foreign_exports_2019 - foreign_exports_1996) / foreign_exports_2019

# foreign exports as share of total production
exports_percents <- dom_source_ts %>%
  group_by(year) %>%
  mutate(total_export = sum(live_weight_t, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(export_percent = 100 * live_weight_t / total_export)

exports_percents_no_error <- dom_source_ts %>%
  filter(dom_source != "error export") %>%
  group_by(year) %>%
  mutate(total_export = sum(live_weight_t, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(export_percent = 100 * live_weight_t / total_export)

foreign_export_percent_1996 <- exports_percents %>%
  filter(dom_source == "foreign export") %>%
  filter(year == 1996) %>%
  pull(export_percent)

foreign_export_percent_2019 <- exports_percents %>%
  filter(dom_source == "foreign export") %>%
  filter(year == 2019) %>%
  pull(export_percent)

foreign_export_percent_1996_no_error <- exports_percents_no_error %>%
  filter(dom_source == "foreign export") %>%
  filter(year == 1996) %>%
  pull(export_percent)

foreign_export_percent_2019_no_error <- exports_percents_no_error %>%
  filter(dom_source == "foreign export") %>%
  filter(year == 2019) %>%
  pull(export_percent)
```

@@

Foreign exports changed by `r round(foreign_exports_percent_change, digits = 1)`% (from `r round(foreign_exports_1996/1000000, digits = 2)` million tonnes in 1996 to `r round(foreign_exports_2019/1000000, digits = 2)` million tonnes in 2019).

As a share of exports (error exports included), foreign exports increased by `r round(100*(foreign_export_percent_2019-foreign_export_percent_1996)/foreign_export_percent_1996, digits = 1)`% from `r round(foreign_export_percent_1996, digits = 1)`% in 1996 to `r round(foreign_export_percent_2019, digits = 1)`% in 2019.

As a share of exports (error exports NOT included), foreign exports increased by `r round(100*(foreign_export_percent_2019_no_error-foreign_export_percent_1996_no_error)/foreign_export_percent_1996_no_error, digits = 1)`% from `r round(foreign_export_percent_1996_no_error, digits = 1)`% in 1996 to `r round(foreign_export_percent_2019_no_error, digits = 1)`% in 2019.
